---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# arce00

<!-- badges: start -->
[![R build status](https://github.com/paleolimbot/arce00/workflows/R-CMD-check/badge.svg)](https://github.com/paleolimbot/arce00/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/arce00/branch/master/graph/badge.svg)](https://codecov.io/gh/paleolimbot/arce00?branch=master)
<!-- badges: end -->

The goal of arce00 is to read e00 files or convert them to a form that sf or sp can read. While these package *can* read e00 files, the read operation is too slow to be practical on some platforms. This package ports the [AVCE library](http://avce00.maptools.org/avce00/avce00.html) to R for efficient conversion to a binary coverage (for which sf/sp read operations are efficient).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/arce00")
```

The arce00 package contains compiled code, so you will need to have build tools (e.g., Rtools) installed.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(arce00)
e00 <- system.file("e00/cis_20170911.e00", package = "arce00")
e00_read_sf(e00)
```

You can also use `e00_layers()` to list layer information and `e00_readOGR()` to read to sp. These functions generate temporary binary coverages under the hood and delete them afterward: to do this conversion yourself, use `e00_convert()`:

```{r}
cov <- e00_temp_coverage()
coverage <- e00_convert(e00, cov)
sf::read_sf(coverage, layer = "LAB")
```
