---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# arce00

<!-- badges: start -->
<!-- badges: end -->

The goal of arce00 is to read e00 files or convert them to a form that sf or sp can read. While these package *can* readn e00 files, the read operation is too slow to be practical on some platforms. This package ports the [AVCE library](http://avce00.maptools.org/avce00/avce00.html) to R for efficient conversion to a binary coverage (for which sf/sp read operations are efficient).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paleolimbot/arce00")
```

The arce00 package contains compiled code, so you will need to have build tools (e.g., Rtools) installed.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(arce00)

e00 <- system.file("e00/cis_20170911.e00", package = "arce00")
cov <- e00_temp_coverage()
coverage <- e00_convert(e00, cov)
sf::read_sf(coverage, layer = "LAB")
```
